---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# copertura

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/copertura?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/copertura)[![Travis-CI Build Status](https://travis-ci.org/njtierney/copertura.svg?branch=master)](https://travis-ci.org/njtierney/copertura)

The goal of copertura is to make it easy to solve the binary optimisation problem known as the "maximal covering location problem" as described by [Church](http://www.geog.ucsb.edu/~forest/G294download/MAX_COVER_RLC_CSR.pdf). Currently it uses the `lp` solver from the `lpsolve` package.

# Why copertura?

It is named "copertura" as this means "coverage" in Italian, and the research problem that created the need for this package is in Ticino, the Italian speaking canton of Switzerland.

<!-- At this stage I'm strongly considering a renaming - perhaps to `maxcovr` - **max**imum **cov**erage in **r**. -->

# How to Install

```{r install, eval = FALSE}

# install.packages("devtools")
devtools::install_github("njtierney/copertura")

```

<!-- # Example Usage -->
<!-- Need to find a good example dataset to use here -->

# Usage

```{r}




```


# Speed

At the moment the main function, `max_coverage` is not super fast, but I will be providing more scalable methods by formulating the model using something like  [`ompr`](https://github.com/dirkschumacher/ompr), which will give users their own choice of solver, in case they want to use something proprietary like `CPLEX`. In the future I will also be looking to create a solver using the `gurobi` interface.

# Known Issues

This is still in beta, so there are likely to be unidentified bugs, please keep this in mind!

# Future Work

Future work aims to provide functions that simplify the data transformations you need to do, and to keep your work in a dataframe, and provide summaries of current coverage, improvement in coverage, and more. Also on the cards are some standardized plots for exploration of data and results.

