---
title: "Using maxcovr"
author: "Nicholas Tierney"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

maxcovr provides tools to make it easy to solve the "maximum covering location problem", a binary optimisation problem described by [Church](http://www.geog.ucsb.edu/~forest/G294download/MAX_COVER_RLC_CSR.pdf). Currently it uses the `lp` solver from the `lpsolve` package.

This vignette aims to get users started with using maxcovr. Other vignettes are provided in the package:

- "Cross Validation with maxcovr", which explains how to perform and interpret cross validation results in a maximum covering location framework
- "Understanding the maximum covering location problem"
- other (perhaps soon to be released vignettes).

This vignette first explains the motivation behind maxcovr, briefly introduces the maximum covering location problem with some real data, and explains how to explore current coverage, and improve it using maxcovr, and interpret the results.

# Why maxcovr

maxcovr was created to make it easy for a non expert to correctly solve the maximum covering location problem. This problem is beginning to be applied in problems in AED placement around the world. However, many of the implementations in papers commercial software such as AMPL, Gurobi, or CPLEX. Additionally, the code that they use in the paper to implement the optimisation is not provided and has to be requested. As a result, these analyses are more difficult to implement and more difficult to reproduce.

maxcovr was created to address these shortcomings, using:

- R, a free and open source language
- An source solver, lpSolve, that can be used on Linux, Windows, and OSX.
- Real-world, open source example data.
- Tidyverse principles to make it easy to use, code, and extend.

As a result of this, results are easy to implement, reproduce, and extend.

<!-- - Providing code and a simple tidy syntax that can be applied to datasets of similar structure -->
<!-- - Making the package source available on GitHub and CRAN. -->
<!-- - Providing example open source datasets that can be used and tested. -->

# The problem

Disclaimer: The following is a fictitious example using real world data.

Consider the toy example where we are playing a tower defense game and we need to place crime surveillance towers to detect crime. 

We have two datasets, `york`, and `york_crime`:

- `york` contains listed building GPS locations in the city of York, provided by the city of york 
- `york_crime` contains a set of crime data from the [`ukpolice`  package](https://www.github.com/njtierney/ukpolice), containing crime data from September 2016.

In this game we already have a few towers built, which are placed on top of the listed buildings with a grade of I. We will call this dataset `york_selected`, and the remaining building locations `york_unselected`

```{r york-towers}

library(maxcovr)
library(dplyr)

# subset to be the places with towers built on them.
york_selected <- york %>% filter(grade == "I")

york_unselected <- york %>% filter(grade != "I")

```

The purpose of the game is to build towers in places so that they are within 100m of crime. We are going to use the crime data that we have to help us choose ideal locations to place towers.

This can be illustrated with the following graphic, where the red circles indicate the current coverage of the building locations, so those blue crimes within the circles are within the coverage.

```{r leaflet, echo = FALSE}

library(leaflet)

leaflet() %>%
    addCircleMarkers(data = york, 
                     radius = 1,
                     color = "steelblue") %>%
    addCircles(data = york_selected, 
               radius = 100,
               stroke = TRUE,
               fill = NULL,
               opacity = 0.8,
               weight = 2,
               color = "coral") %>%
    # addTiles() %>%
    addProviderTiles("CartoDB.Positron") %>%
    setView(lng = median(york$long),
            lat = median(york$lat),
            zoom = 15)

```

Currently the coverage looks alright, but let's verify the coverage using the `nearest` function. `nearest` takes two dataframes and returns the nearest lat/long coords from the first dataframe to the second dataframe, along with the distances between them and the appropriate columns from the building dataframe.

```{r}

dat_dist <- york_selected %>% nearest(york_crime)

head(dat_dist)

```

You can instead return a dataframe which has every building in the rows, and the nearest crime to the building, by simply changing the order.

```{r}

dat_dist_bldg <- york_crime %>% nearest(york_selected)
head(dat_dist_bldg)
```

To evaluate the coverage we can use `summarise_coverage`

```{r}

dat_dist %>% 
    mutate(is_covered = distance <= 100) %>%
    summarise_coverage()

```

This tells us that out of all the crime, 18.68% of it is within 100m, 339 crimes are covered, but the mean distance to the surveillance camera is 1400m.

# maximising coverage

We can maximise the coverage

# using max_coverage


- Putting result output in a dataframe (because like Jenny Bryan says [if you can, you probably should](https://www.youtube.com/watch?v=4MfUCX_KpdE&list=PLR7d32uh__xbrzSdfzxxCxCEFQnt7BcOj&index=2)). 
- Adhering to [tidyverse]() principles, to make it easy to code and think about.

# Interpreting results

# Further reading

You can read the other vignettes...

Also recommended are the resources ...


<!-- ## Vignette Info -->

<!-- Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette. -->

<!-- ## Styles -->

<!-- The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows: -->

<!--     output:  -->
<!--       rmarkdown::html_vignette: -->
<!--         css: mystyles.css -->

<!-- ## Figures -->

<!-- The figure sizes have been customised so that you can easily put two images side-by-side.  -->
<!-- You can enable figure captions by `fig_caption: yes` in YAML: -->

<!--     output: -->
<!--       rmarkdown::html_vignette: -->
<!--         fig_caption: yes -->

<!-- Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**. -->

<!-- ## More Examples -->

<!-- You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`. -->

<!-- ```{r, echo=FALSE, results='asis'} -->
<!-- knitr::kable(head(mtcars, 10)) -->
<!-- ``` -->

<!-- Also a quote using `>`: -->

<!-- > "He who gives up [code] safety for [code] speed deserves neither." -->
<!-- ([via](https://twitter.com/hadleywickham/status/504368538874703872)) -->
